\section{Joda Time}
Joda Time~\cite{jodatime} is a Java date and time API.
It provides a quality replacement for the Java date and time classes.
%We used this API because the Java Date and Calendar classes are badly designed.
\salespoint incorporates Joda Time, because it is open source, easy to use and offers better performance characteristics than Java date and time classes.

Key concepts from Joda Time used in \salespoint{} are \textit{Instant}, \textit{Interval}, \textit{Duration} and \textit{Period}.
From Joda Time documentation:
\begin{quote}
The most frequently used concept in Joda-Time is that of the \textit{instant}.
An Instant is defined as \textit{an instant in the datetime continuum specified as a number of milliseconds from 1970-01-01T00:00Z}.
This definition of milliseconds is consistent with that of the JDK in \code{Date} or \code{Calendar}.
Interoperating between the two APIs is thus simple.
\end{quote}

\textit{Intervals} are defined by two Instants.
An Interval is \textit{half-open}, that is to say the start is inclusive but the end is not.
Also, the end is always greater or equal than the start.

\textit{Durations} in Joda Time represent a duration in time, exact to the milisecond.
Durations can be thought of as length of an Interval.

\textit{Periods} also represent durations in time, but in a more abstract way.
A Period may be a month, which may be 28, 29, 30 or 31 days, thus the length in miliseconds of those periods differ.

If you, for example have an Instant of February, 1st and add a Period of one month, the result will be an Instant of March, 1st.
Adding instead a Period of 30 days to an Instant of February, 1st will result in an Instant of March, 2nd or March 3rd, depending if the Instant is in a leap year or not.
